### 2024-03-11 docs/manuscript/manuscript.qmd
a citation was corrected

However, the mediating analysis showed that total muscle mass diminished the main observed effect of body fat on physical fitness, with more muscled individuals displaying a better physical performance despite the body fat percentage. This finding suggests that older adults could be benefited of activities that promotes their muscle mass conservation, even when they have high body fat percentages [pmid:27663845].  Nevertheless, caution is advised in the interpretation of this result, as the close physiological association among increasing body fat and decreasing muscle mass during aging have been well-studied [@pmid:33335909]

>>>>

However, the mediating analysis showed that total muscle mass diminished the main observed effect of body fat on physical fitness, with more muscled individuals displaying a better physical performance despite the body fat percentage. This finding suggests that older adults could be benefited of activities that promotes their muscle mass conservation, even when they have high body fat percentages [@pmid:27663845].  Nevertheless, caution is advised in the interpretation of this result, as the close physiological association among increasing body fat and decreasing muscle mass during aging have been well-studied [@pmid:33335909]
